A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2020-11-25 kobakian-cook.Rmd
almost ready for submission

The buffer distance, hexagon size, hexagon amount to filter and width of angle are parameters that will be determined within \code{create_hexmap()}, if they are not provided. They are created as they are needed throughout the following example.

>>>>

The buffer distance, hexagon size, hexagon amount to filter and width of angle are parameters that will be determined within `create_hexmap()`, if they are not provided. They are created as they are needed throughout the following example.

### 2020-11-25 kobakian-cook.tex
almost ready for submission

The algorithm is implemented in the \texttt{sugarbag} package for
\texttt{R}, named after the common name for the \emph{Trigona
carbonaria} bee -- a species which builds flat layers of hexagonal brood
cells, spiralling out from a central point \citep{PH}. This unusual
pattern also provided the inspiration for the algorithm, where the maps
are constructed by building out from multiple focal points on the
geographic map base in a spiral fashion.

@@

The \texttt{sugarbag} package contains a set of functions that help R
users to create a hexagon tile map. The algorithm presented in the
\texttt{sugarbag} package operates on a set of simple feature geometry
objects , known as \texttt{sf} objects\citep{sf}. This package allows R
users to create \texttt{sf} objects by importing polygons stored in
various formats. Users should provide a set of polygons that define
geographic units by their administrative boundaries. The functions
arrange the geographic units in order of proximity to a set of locations
provided, such as the centre of major cities. The centroid location of
each geographic unit is used to measure the proximity. It emphasises the
major cities as population hubs, rather than emphasizing the size of
large, rural geographic units.

@@

The set of SA2 polygons for Tasmania, using the 2011 definition of SA2s,
is accessed from the \texttt{absmapsdata} package. A single column of
the data set is used to identify the unique areas. In this case, the
unique SA2 names for each SA2 have been used.

@@

\begin{Schunk}
\begin{figure}
\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/filterprocess-1} \caption[Illustration of several steps of the algorithm]{Illustration of several steps of the algorithm: (a) ... (b) ... (c) ... (d). }\label{fig:filterprocess}
\end{figure}
\end{Schunk}

>>>>

The algorithm is implemented in the \CRANpkg{sugarbag} package for
\texttt{R}, named after the common name for the \emph{Trigona
carbonaria} bee -- a species which builds flat layers of hexagonal brood
cells, spiralling out from a central point \citep{PH}. This unusual
pattern also provided the inspiration for the algorithm, where the maps
are constructed by building out from multiple focal points on the
geographic map base in a spiral fashion.

@@

The \pkg{sugarbag} package contains a set of functions that help R users
to create a hexagon tile map. The algorithm presented in the
\pkg{sugarbag} package operates on a set of simple feature geometry
objects , known as \CRANpkg{sf} objects\citep{sf}. This package allows R
users to create \pkg{sf} objects by importing polygons stored in various
formats. Users should provide a set of polygons that define geographic
units by their administrative boundaries. The functions arrange the
geographic units in order of proximity to a set of locations provided,
such as the centre of major cities. The centroid location of each
geographic unit is used to measure the proximity. It emphasises the
major cities as population hubs, rather than emphasizing the size of
large, rural geographic units.

@@

The set of SA2 polygons for Tasmania, using the 2011 definition of SA2s,
is accessed from the \pkg{absmapsdata} package. A single column of the
data set is used to identify the unique areas. In this case, the unique
SA2 names for each SA2 have been used.

@@

\begin{Schunk}
\begin{figure}
\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/filterprocess-1} \caption[Illustration of key steps of the algorithm]{Illustration of key steps of the algorithm: (a) full hexagon grid is created first; (b) buffer is applied, shown as dark green circles, to accommodate irregularly shaped regions; (c, d) allocation process, relative the center of Hobart, showing the 8th centroid to be allocated. The relationship between Hobart (the cross) and the centroid (the purple triangle) is used to filter the potential locations from the grid within a wedge. Hexagons already allocated are shown in black, and the purple circle indicates the hexagon to be assigned to the 8th centroid.}\label{fig:filterprocess}
\end{figure}
\end{Schunk}
